\documentclass[12pt]{letter}

\usepackage{url}
\usepackage[margin=1in]{geometry}


\makeatletter
\let\@texttop\relax
\makeatother

\address{722 South Main Street\\
  Apt.~B1\\
  Harrisonburg, VA 22801}
\signature{John H.~Johnson}

\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}

\begin{document}
\begin{letter}{}
\opening{Dr. so-and-so}

I am a fifth year PhD candidate in the mathematics department at
Howard University with an expected graduation date of May 2011.  
I learned about the $\la\mbox{program}\ra$ at your
$\la\mbox{university}\ra$ via \url{mathjobs.org}. 
This fellowship/program  and location sounds like a great opportunity
for mathematical research and outreach. 
Therefore, I am submitting my application for consideration for the 
$\la\mbox{program}\ra$.

My research interest is focused on the interplay between topological
algebra and Ramsey Theory. 
Neil Hindman is my advisor at Howard University. 
As my CV states, I have presented at several conferences and given an
invited talk at James Madison University. 
Additionally, my CV demonstrates that I have several years teaching
experience and general mathematical outreach. 

Currently I do not have any published papers, therefore in lieu of  
a publication list I have included a writing sample.
This writing sample is a draft of a research paper I plan to submit by
the end of the Spring 2011 semester.
In addition, I invite you, and any one else on the application
committee, to see my research presentation at the New Orleans Joint
Mathematics Meeting.
I will be presenting January 6 at 10:15am on the 2nd floor of the
Marriott in room La Galerie 5. 

Thank you for your time and consideration. 
I look forward to hearing from you. 
\closing{Sincerely,}
 
\encl{cover letter, curriculum vitae, research statement, teaching
  statement, and writing sample}

\end{letter}
\end{document}
